---
title: "Mapping raw reads"
author: "Søren Helweg Dam"
date: "2022-08-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data 

Data used is from [Zhang et. al, 2019](https://doi.org/10.1016/j.gpb.2018.12.008).


### Downloading the data

Raw reads

```{sh, eval=FALSE}

for id in {1..8}
do
  wget ftp://download.big.ac.cn/gsa/CRA000746/CRR02597${id}/CRR02597${id}_f1.fq.gz
  wget ftp://download.big.ac.cn/gsa/CRA000746/CRR02597${id}/CRR02597${id}_r2.fq.gz
done
```


## fastp preprocessing

```{sh}
alias fastp='/home/ctools/fastp/fastp'
mkdir trimmed

for id in {1..8}
do
forward=CRR02597${id}_f1.fq.gz
reverse=CRR02597${id}_r2.fq.gz

fastp -i fastq/$forward -I fastq/$reverse -o trimmed/$forward -O trimmed/$reverse --detect_adapter_for_pe -c --cut_front --cut_right
done

```




[Ensembl Transcriptomes v96](https://github.com/pachterlab/kallisto-transcriptome-indices/releases)

```{sh, eval=FALSE}
wget https://github.com/pachterlab/kallisto-transcriptome-indices/releases/download/ensembl-96/homo_sapiens.tar.gz

tar -xf homo_sapiens.tar.gz

rm homo_sapiens.tar.gz
 
```

## STAR ----

```{sh}
# Download assembly reference
cd homo_sapiens
# wget ftp://ftp.ensembl.org/pub/release-77/fasta/homo_sapiens/dna/Homo_sapiens.GRCh38.dna.primary_assembly.fa.gz
wget http://ftp.ensembl.org/pub/release-107/fasta/homo_sapiens/dna/Homo_sapiens.GRCh38.dna_sm.primary_assembly.fa.gz

wget http://ftp.ensembl.org/pub/release-107/gtf/homo_sapiens/Homo_sapiens.GRCh38.107.gtf.gz

gunzip *.gz

mkdir ../ref

# Index genome
STAR --runMode genomeGenerate --genomeDir ../ref/ --genomeFastaFiles Homo_sapiens.GRCh38.dna_sm.primary_assembly.fa --sjdbGTFfile Homo_sapiens.GRCh38.107.gtf --runThreadN 8

mkdir mapped
cd trimmed
for id in {1..8}
do
forward=CRR02597${id}_f1.fq.gz
reverse=CRR02597${id}_r2.fq.gz
STAR --runMode alignReads --runThreadN 8 --genomeDir ../ref/ --outSAMtype BAM SortedByCoordinate --readFilesIn ${forward} ${reverse} --readFilesCommand gunzip -c --outFileNamePrefix ../mapped/CRR02597${id}
done

cd ../mapped
mkdir ../bam
mv *.bam ../bam
cd ../bam
for file in *.bam
do
samtools index $file
done
```

## BAM ----

```{sh}
echo "ID  File  Patient Color
CRR025973	/home/projects/shd/relapseR/raw_data/bam/CRR025973Aligned.sortedByCoord.out.bam	Patient_A	1
CRR025971	/home/projects/shd/relapseR/raw_data/bam/CRR025971Aligned.sortedByCoord.out.bam	Patient_B	3
CRR025977	/home/projects/shd/relapseR/raw_data/bam/CRR025977Aligned.sortedByCoord.out.bam	Patient_C	5
CRR025975	/home/projects/shd/relapseR/raw_data/bam/CRR025975Aligned.sortedByCoord.out.bam	Patient_D	7
CRR025974	/home/projects/shd/relapseR/raw_data/bam/CRR025974Aligned.sortedByCoord.out.bam	Patient_A	2
CRR025972	/home/projects/shd/relapseR/raw_data/bam/CRR025972Aligned.sortedByCoord.out.bam	Patient_B	4
CRR025978	/home/projects/shd/relapseR/raw_data/bam/CRR025978Aligned.sortedByCoord.out.bam	Patient_C	6
CRR025976	/home/projects/shd/relapseR/raw_data/bam/CRR025976Aligned.sortedByCoord.out.bam	Patient_D	8" > /home/projects/shd/relapseR/raw_data/bam/bam_list.tsv
# rm /home/projects/shd/relapseR/raw_data/bam/bam_list.tsv
# vim /home/projects/shd/relapseR/raw_data/bam/bam_list.tsv
```


## Count mapped reads

```{sh}
for file in *.bam
do 
samtools view -c -F 4 $file
done
```


## Sashimi plot

```{sh}
cd /home/projects/shd/tools/

echo "#4EEE94
#FF0000
#FFA500
#0000FF
#8FBC8F
#CD6090
#EECFA1
#9FB6CD" > ../relapseR/raw_data/bam/colors.tsv

python ggsashimi.py -b ../relapseR/raw_data/bam/bam_list.tsv -c 16:28931696-28933634 -o ../relapseR/figs/sashimi -g ../relapseR/raw_data/homo_sapiens/Homo_sapiens.GRCh38.107.gtf -L 3 -P ../relapseR/raw_data/bam/colors.tsv -C 4 --base-size 22

```



## Junction identification

```{sh}
ref=homo_sapiens/Homo_sapiens.GRCh38.dna_sm.primary_assembly.fa

for id in {1..8}
do
file=bam/*${id}A*.bam
# portcullis full -t 8 $ref $file -o portcullis/CRR02597${id}

# Regtools annotate junctions
regtools junctions annotate -S -o portcullis/CRR02597${id}/annotated_junctions.tsv portcullis/CRR02597${id}/3-filt/portcullis_filtered.pass.junctions.bed homo_sapiens/Homo_sapiens.GRCh38.dna_sm.primary_assembly.fa homo_sapiens/Homo_sapiens.GRCh38.107.gtf
done

junctool set --union 






```




## Exon counts ----

```{r, eval=FALSE}

# https://nov2020.archive.ensembl.org/Homo_sapiens/Transcript/Exons?db=core;g=ENSG00000177455;r=16:28931965-28939342;t=ENST00000565089
annotation <- data.frame(
  GeneID = c("CD19:Exon1", "CD19:Exon2", "CD19:Exon3", "CD19:Exon4"),
  Chr = "chr16",
  Start = c(28931965, 28932346,28932910, 28933234),
  End = c(28932088, 28932612, 28933114, 28933509),
  Strand = "+",
  stringsAsFactors = FALSE
)
annotation


library("Rsubread")

files <- list.files("raw_data/bam/", pattern = "*.bam$", full.names = TRUE)

exon_counts <- featureCounts(
  files = files,
  annot.ext = annotation,
  isPairedEnd=TRUE,
  nthreads = 8,
  juncCounts = TRUE
  )

saveRDS(exon_counts, "raw_data/exon_counts.RDS")
exon_counts <- readRDS("raw_data/exon_counts.RDS")

library("dplyr")
library("tidyr")
counts <- tibble::as_tibble(exon_counts$counts, rownames = "exon")
colnames(counts) <- c("Exon", "B0", "B14", "A0", "A14", "D0", "D14", "C0", "C14")

counts %>% 
  pivot_longer(cols = -Exon, names_to = "Patient", values_to = "Counts") %>% 
  pivot_wider(names_from = "Exon", values_from = Counts) %>% 
  mutate(PSI = `CD19:Exon2`/(`CD19:Exon1` + `CD19:Exon2` + `CD19:Exon3` + `CD19:Exon4`),
         Response = c("NR", "NR", "Relapse", "Relapse", "Remission", "Remission", "Relapse", "Relapse")) %>% 
  arrange(Patient)

```

## Snapcount

```{r}
# https://www.ensembl.org/Homo_sapiens/Transcript/Exons?db=core;g=ENSG00000177455;r=16:28931971-28939342;t=ENST00000538922
library("snapcount")
library("magrittr")
library("dplyr")
library("ggplot2")

A <- QueryBuilder(compilation = "srav2", region = "chr16:28931965-28933114") %>% 
  set_row_filters(strand == "+") %>% set_coordinate_modifier(Coordinates$Within)

B <- QueryBuilder(compilation = "srav2", region = "chr16:28932346-28932612") %>% 
  set_row_filters(strand == "+") %>% set_coordinate_modifier(Coordinates$Within)

jir <- junction_inclusion_ratio(list(A),
                              list(B),
                              group_names=c("groupA","groupB"))

## TCGA - intron2
#left inclusion query
lqi2 <- QueryBuilder(compilation="tcga",  regions="chr16:28932346-28932612") %>%  # Exon2
  # set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Within)
#right inclusion query
rqi2 <- QueryBuilder(compilation="tcga", regions="chr16:28932911-28933114") %>% # Exon3
  # set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Within)
#exclusion query
exi2 <- QueryBuilder(compilation="tcga", regions="chr16:28932613-28932910") %>% # Intron2
  # set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Within)

psi_tcgai2 <- percent_spliced_in(list(lqi2), list(rqi2), list(exi2), min_count=20)

jir <- junction_inclusion_ratio(list(rqi2),
                              list(exi2),
                              group_names=c("groupA","groupB"))
# 28932615

## TCGA
#Build new query against GTEx
#left inclusion query
lq <- QueryBuilder(compilation="tcga", regions="chr16:28931971-28932088") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)
#right inclusion query
rq <- QueryBuilder(compilation="tcga", regions="chr16:28932613-28932910") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)
#exclusion query
ex <- QueryBuilder(compilation="tcga", regions="chr16:28932089-28932910") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)

psi_tcga <- percent_spliced_in(list(lq), list(rq), list(ex), min_count=20)
#order by psi descending


## TCGA
#Build new query against GTEx
#left inclusion query
lq <- QueryBuilder(compilation="tcga", regions="chr16:28932089-28932345") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)
#right inclusion query
rq <- QueryBuilder(compilation="tcga", regions="chr16:28932613-28932910") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)
#exclusion query
ex <- QueryBuilder(compilation="tcga", regions="chr16:28932089-28932910") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)

psi_tcga <- percent_spliced_in(list(lq), list(rq), list(ex), min_count=20)

jir2 <- junction_inclusion_ratio(list(lq),
                              list(ex),
                              group_names=c("groupA","groupB"))
#order by psi descending
# psi <- psi[order(-psi),]
# head(psi)






md <- snapcount:::get_compilation_metadata(compilation = "tcga")
metadata <- tibble::tibble(sample_id = md$rail_id, 
                           Cancer=md$gdc_cases.tissue_source_site.project,
                           project = md$gdc_cases.project.project_id,
                           Tissue = md$gdc_cases.project.primary_site,
                           sample_code = md$gdc_cases.samples.submitter_id,
                           gender = md$gdc_cases.demographic.gender,
                           outcome = md$cgc_case_primary_therapy_outcome_success,
                           tumor_status = md$cgc_case_tumor_status,
                           age = md$xml_age_at_initial_pathologic_diagnosis,
                           vital = md$cgc_case_vital_status) |> 
  dplyr::filter(
    stringr::str_detect(stringr::str_to_lower(Cancer), "lymph")
    ) 

# filter(metadata, stringr::str_detect(stringr::str_to_lower(Cancer), "lymphoma"))


psi_BALL <- psi_tcga %>% 
  dplyr::filter(psi != -1) %>% 
  semi_join(metadata, by="sample_id") %>% 
  left_join(metadata, by="sample_id") %>% 
  mutate(type = "TCGA DLBCL")
View(psi_BALL)

# Sample data
psi_low <- dplyr::filter(psi_BALL$psi < 0.95)
psi_high <- dplyr::filter(psi_BALL, psi >= 0.95)
group <- c(rep("Low", 50), rep("Group2", 50))

ages <- c(rnorm(50, mean = 30, sd = 5), rnorm(50, mean = 35, sd = 6))

# Boxplot
boxplot(ages ~ group, main = "Age Distribution by Group", xlab = "Group", ylab = "Age")


psi_tcga_all <- psi_tcga %>% filter(psi != -1) %>% anti_join(metadata, by="sample_id") %>% mutate(type = "TCGA (Remaining)")

## GTEx
#Build new query against GTEx
#left inclusion query
lq <- QueryBuilder(compilation="gtexv2", regions="chr16:28932089-28932345") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)
#right inclusion query
rq <- QueryBuilder(compilation="gtexv2", regions="chr16:28932613-28932910") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)
#exclusion query
ex <- QueryBuilder(compilation="gtexv2", regions="chr16:28932089-28932910") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)

psi_gtex <- percent_spliced_in(list(lq), list(rq), list(ex), min_count=20)
#order by psi descending
# psi <- psi[order(-psi),]
# head(psi)

# psi_gtex %>% filter(psi != -1) %>% pull(psi) %>% qplot

psi_BALLi2 <- jir %>% 
  # dplyr::filter(psi != -1) %>% 
  semi_join(metadata, by="sample_id") %>% 
  left_join(metadata, by="sample_id") %>% 
  mutate(type = "TCGA DLBCL")
jir_BALL <- jir2 %>% 
  # dplyr::filter(psi != -1) %>% 
  semi_join(metadata, by="sample_id") %>% 
  left_join(metadata, by="sample_id") %>% 
  mutate(type = "TCGA DLBCL")
hist(jir_BALL$jir)

ts <- tissue_specificity(list(lq,rq, ex))
blood_sample <- ts %>% filter(tissue == "Blood")
bm_sample <- ts %>% filter(tissue == "Bone Marrow")
spleen_sample <- ts %>% filter(tissue == "Spleen")


psi_gtex_blood <- psi_gtex %>% filter(psi != -1) %>% 
  semi_join(blood_sample, by="sample_id") %>% 
  mutate(type = "GTEx Blood")

psi_gtex_bm <- psi_gtex %>% filter(psi != -1) %>% 
  semi_join(blood_sample, by="sample_id") %>% 
  mutate(type = "GTEx Bone Marrow")


psi_gtex_spleen <- psi_gtex %>% filter(psi != -1) %>% 
  semi_join(spleen_sample, by="sample_id") %>% 
  mutate(type = "GTEx Spleen")


## SRA

md_sra <- snapcount:::get_compilation_metadata(compilation = "srav3h") |> 
  dplyr::filter(library_layout == "paired")

md_sra |> dplyr::filter(stringr::str_detect(study_title, "B-ALL")) |> dim()
md_sra |> dplyr::filter(stringr::str_detect(study_title, "DLBCL")) |> dim()
md_sra |> dplyr::filter(stringr::str_detect(study_title, "lymph node")) |> dim()


lq <- QueryBuilder(compilation="srav3h", regions="chr16:28932089-28932345") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)
#right inclusion query
rq <- QueryBuilder(compilation="srav3h", regions="chr16:28932613-28932910") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)
#exclusion query
ex <- QueryBuilder(compilation="srav3h", regions="chr16:28932089-28932910") %>% 
  set_row_filters(strand == "+") %>% 
  set_coordinate_modifier(Coordinates$Exact)

psi_sra <- percent_spliced_in(list(lq), list(rq), list(ex), min_count=20)

md_sra_ball <- md_sra |> 
  dplyr::filter(stringr::str_detect(study_title, "B-ALL"))
psi_sra_ball <- psi_sra %>% 
  dplyr::filter(psi != -1) %>% 
  semi_join(md_sra_ball, by=c("sample_id" = "rail_id")) %>% 
  mutate(type = "SRA B-ALL")

md_sra_aml <- md_sra |> 
  dplyr::filter(stringr::str_detect(study_title, "AML"))
psi_sra_aml <- psi_sra %>% 
  dplyr::filter(psi != -1) %>%
  semi_join(md_sra_aml, by=c("sample_id" = "rail_id")) %>% 
  mutate(type = "SRA AML")

md_sra_dlbcl <- md_sra |> 
  dplyr::filter(stringr::str_detect(study_title, "DLBCL"))
psi_sra_dlbcl <- psi_sra %>% 
  dplyr::filter(psi != -1) %>%
  semi_join(md_sra_dlbcl, by=c("sample_id" = "rail_id")) %>% 
  mutate(type = "SRA DLBCL")


library(ggridges)
colors <- c("hotpink3", "darkblue", "slategray", "red", "purple", "slategray", "darkblue")
psi_plot <- #psi_tcga_all %>% 
  psi_BALL %>%
  # bind_rows(psi_sra_ball) |>
  # bind_rows(psi_sra_aml) |>
  # bind_rows(psi_sra_dlbcl) |>
  # anti_join(psi_BALL, by = "sample_id") %>%
  bind_rows(psi_BALL) %>%
  bind_rows(psi_BALLi2) %>%
  bind_rows(psi_gtex_blood) %>%
  bind_rows(psi_gtex_spleen) %>%
  # bind_rows(psi_gtex %>% filter(psi != -1) %>% anti_join(blood_sample, by="sample_id") %>% mutate(type = "GTEx (Remaining)")) %>%
  ggplot()+
  aes(x = psi, fill = type, color = type, y = type) +
  # geom_histogram() +
  geom_density_ridges(alpha = 0.4, quantile_lines = TRUE, quantiles = 2) +
  theme_classic(base_size = 18) +
  scale_fill_manual(values = colors) +
  scale_color_manual(values = colors) +
  labs(color = "Tissue",
       fill = "Tissue",
       x = "Fraction of CD19 transcripts containing Exon2.",
       y = "") +
  theme(legend.position="none") +
  xlim(0.6, 1.05)
psi_plot
ggsave(psi_plot, filename = "../figs/PSI_TCGA.png", width = 10, height = 4)

```


## TCGA download

### Metadata

```{sh}
wget https://tcga-xena-hub.s3.us-east-1.amazonaws.com/download/survival%2FDLBC_survival.txt
```
```{r}
md <- readr::read_table("GDCdata/survival%2FDLBC_survival.txt")

seed=555
md <- md %>% 
  slice_sample(n=10)
barcodes <- md$sample
```

# PSI

```{r}
library(TCGAbiolinks)

query <- GDCquery(
    project = "TCGA-DLBC",
    data.category = "Gene expression",
    data.type = "Exon quantification",
    # platform = "Illumina HiSeq",
    # file.type  = "normalized_results",
    # experimental.strategy = "RNA-Seq",
    barcode = metadata$sample_code,
    legacy = TRUE
)
GDCdownload(
    query = query,
    method = "api"
)
data <- GDCprepare(query = query,
                   directory = "GDCdata")
psi <- tibble::as_tibble(
  SummarizedExperiment::assay(
  data[rownames(data) %in% c("chr16:28943260-28943409:+", "chr16:28943667-28943933:+", "chr16:28944232-28944435:+"),]
  )
) %>% 
  mutate(exon = c("CD19:Exon1","CD19:Exon2","CD19:Exon3")) %>% 
  tidyr::pivot_longer(starts_with("TCGA"), names_to = "sample", values_to = "counts") %>% 
  tidyr::pivot_wider(names_from = exon, values_from = counts) %>% 
  mutate(PSI = `CD19:Exon2`/(`CD19:Exon1`+`CD19:Exon2`+`CD19:Exon3`))

psi <- psi %>% 
  mutate(patient = colData(data)$patient) %>% 
  left_join(md, by = c("patient" = "_PATIENT"))

psi %>% 
  ggplot()+
  aes(x = PSI, y = DFI.time, color = DFI) +
  geom_point()

```
```{r}

folders <- list.files("GDCdata/TCGA-DLBC/legacy/Gene_expression/Exon_junction_quantification", full.names = T)


lapply(folders, function(folder){
  
  system(paste0("cat ", folder, "/*.txt | grep chr16 > ", basename(folder), ".txt"))
  
})

junction_counts <- tibble::tibble(junction = c(), raw_counts=c(), sample=c())
data <- lapply(folders, function(folder){
  
  junction_counts <- paste0(basename(folder), ".txt") %>% 
    readr::read_table(col_names = c("junction", "raw_counts")) %>% 
    mutate(sample = basename(folder))
  return(junction_counts)
}) %>% 
  bind_rows()

filter(data, stringr::str_detect(junction, ":2894"),
       # stringr::str_detect(junction, "-", negate = T))
       raw_counts > 0)
```




## fastQC


```{sh}

cd raw_data
for file in *.fq.gz
do
  fastqc $file -o qc
done

```



## Kallisto ----

[Manual](http://pachterlab.github.io/kallisto/manual.html)


Quantify raw reads

```{sh eval=FALSE}

index="homo_sapiens/transcriptome.idx"
<!-- gtf="homo_sapiens/Homo_sapiens.GRCh38.96.gtf" -->

kallisto quant -i $index -o patient_A0 CRR025973_f1.fq.gz CRR025973_r2.fq.gz

kallisto quant -i $index -o patient_A14 CRR025974_f1.fq.gz CRR025974_r2.fq.gz

kallisto quant -i $index -o patient_B0 CRR025971_f1.fq.gz CRR025971_r2.fq.gz

kallisto quant -i $index -o patient_B14 CRR025972_f1.fq.gz CRR025972_r2.fq.gz

kallisto quant -i $index -o patient_C0 CRR025977_f1.fq.gz CRR025977_r2.fq.gz

kallisto quant -i $index -o patient_C14 CRR025978_f1.fq.gz CRR025978_r2.fq.gz

kallisto quant -i $index -o patient_D0 CRR025975_f1.fq.gz CRR025975_r2.fq.gz

kallisto quant -i $index -o patient_D14 CRR025976_f1.fq.gz CRR025976_r2.fq.gz

```

Convert 


## Import into R

```{r, eval=FALSE}
library(IsoformSwitchAnalyzeR)
library(magrittr)

kallistoQuant <- importIsoformExpression(
    parentDir = "raw_data/samples")

# Add genes
tx_gene <- readr::read_tsv("raw_data/homo_sapiens/transcripts_to_genes.tsv", col_names = c("transcript", "ensembl_gene", "gene"))

# Create count matrix
tx_count <- kallistoQuant$counts %>% 
  dplyr::left_join(tx_gene, by = c("isoform_id" = "transcript")) %>% 
  tidyr::unite(col = "gene_tx", gene, isoform_id, sep = ":") %>% 
  dplyr::select(-ensembl_gene) %>% 
  tibble::column_to_rownames("gene_tx") %>% 
  as.matrix() %>% 
  ceiling()

# Create sample data
sampleData <- data.frame(
    sampleID = colnames(tx_count),
    group = colnames(tx_count) %>% 
      stringr::str_extract("[A-D]\\d+") %>% 
      factor(),
    patients = colnames(tx_count) %>% 
      stringr::str_extract("[A-D]")
)



```


```{r}



devtools::load_all("../shd_pairedGSEA/")

paired_A <- pairedGSEA::paired_diff(
  object = tx_count,
  metadata = sampleData,
  group_col = "group", 
  sample_col = "sampleID",
  baseline = "A0", 
  case = "A14", 
  experiment_title = "patient_A",
  run_sva = FALSE)

```


```{r}
library(dplyr)
library(tidyr)

tx_count <- kallistoQuant$counts %>% 
  dplyr::left_join(tx_gene, by = c("isoform_id" = "transcript"))

tx_count %>% as_tibble %>% 
  dplyr::filter(gene == "CD19") %>% 
  select(-ends_with("0"), -ensembl_gene, -gene)
  # mutate(A_lfc = log2((patient_A14+1)/ (patient_A0+1)),
  #        B_lfc = log2((patient_B14+1)/ (patient_B0+1)),
  #        C_lfc = log2((patient_C14+1)/ (patient_C0+1)),
  #        D_lfc = log2((patient_D14+1)/ (patient_D0+1))) %>% 
  # select(-starts_with("patient"), -ensembl_gene)
  pivot_longer(starts_with("patient"), names_to = "patient", values_to = "counts") %>% 
  mutate()
```


* Identify transcripts missing exon 2, 3, or 4
* Differential splicing analysis
* IsoformSwitchAnalyzeR
* 


ENST00000538922

ENST00000324662

ENST00000567541

ENST00000565089

ENST00000567368

ENST00000566890


ENSE00001227623
ENSE00001227618
ENSE00003483648


41 all
89 none
62 all
22 all
90 none
68 none
